FinalManuscript_DISCS_UG

### 2018-06-20 parts/00_abstract.tex
Changed the names and did some formatting fixes

\begin{thesisabstract}
\paragraph{         }This paper is a sample document that serves as a format and content guideline for undergraduate thesis submissions to the Department of Information Systems and Computer Science. In this section, the abstract, the group should be able to give the readers a clear and concise overview of their study. The section should contain the objectives of the thesis, the methods to be used, and when available, the results of the study, the conclusion, and the recommendations for further work, all based on the intended research objectives. A good abstract should be at most around 150-200 words, or half a page. It should also not contain any references, figures, or equations.
\end{thesisabstract}

>>>>

\begin{thesisabstract}
    \noindent
    This paper is a sample document that serves as a format and content guideline for undergraduate thesis submissions to the Department of Information Systems and Computer Science. In this section, the abstract, the group should be able to give the readers a clear and concise overview of their study. The section should contain the objectives of the thesis, the methods to be used, and when available, the results of the study, the conclusion, and the recommendations for further work, all based on the intended research objectives. A good abstract should be at most around 150--200 words, or half a page. It should also not contain any references, figures, or equations.
\end{thesisabstract}
